KidsAIR wood stove grades and usage

### 2020-09-16 exposure_covariate_associations.Rmd
data cleaning and model updates

```{r, eval=TRUE, include=TRUE}
####### Format full data to use for analysis
analysis_data <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  arrange(area, home, sampling_day) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  # dichotomize variables by median value
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  mutate(home_act_door_2level = cut(home_act_door_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_smoke_2level = cut(home_act_smoking_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_windows_2level = cut(home_act_windows_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_sweep_2level = cut(home_act_sweep_sum, breaks = c(0, 3, 7),
                                 labels = c("<3", "3+"),
                                 right = FALSE))

@@

  #print(table(model.frame(analysis_results)$analysis_covar))
  print(nobs(analysis_results))

  tidy_results <<- tidy(analysis_results, conf.int = TRUE) %>% 
    filter(term != '(Intercept)') %>% 
    mutate(Estimate = round((exp(estimate)-1)*100, digits = 2),
           'P-value' = round(p.value, digits = 2),
           'Upper 95% CL' = round((exp(conf.high)-1)*100, digits = 2),
           'Lower 95% CL' = round((exp(conf.low)-1)*100, digits = 2),
           Term = gsub("analysis_covar", paste0(label, ": "), term)) %>% 
    select(Term, Estimate, 'Lower 95% CL', 'Upper 95% CL', 'P-value')

@@

d27 <- analysis_function("moisture_closest", "Wood moisture - closest to sampling")
d28 <- analysis_function("moisture_closest_2level", "Wood moisture - closest to sampling")
d29 <- analysis_function("mean_moisture_winter", "Wood moisture - Winter mean")
d30 <- analysis_function("moisture_winter_2level", "Wood moisture - Winter mean")

>>>>

```{r, eval=TRUE, include=TRUE}
####### Format full data to use for analysis
analysis_data <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  filter(area == "AK") %>% 
  arrange(area, home, sampling_day) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  # dichotomize variables by median value
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  mutate(home_act_door_2level = cut(home_act_door_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_smoke_2level = cut(home_act_smoking_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_windows_2level = cut(home_act_windows_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_sweep_2level = cut(home_act_sweep_sum, breaks = c(0, 3, 7),
                                 labels = c("<3", "3+"),
                                 right = FALSE))

@@

  print(table(model.frame(analysis_results)$analysis_covar))
  print(nobs(analysis_results))

  tidy_results <<- tidy(analysis_results, conf.int = TRUE) %>% 
    filter(term != '(Intercept)') %>% 
    mutate(Estimate = round((exp(estimate)-1)*100, digits = 2),
           'P-value' = round(p.value, digits = 2),
           'Upper 95% CL' = round((exp(conf.high)-1)*100, digits = 2),
           'Lower 95% CL' = round((exp(conf.low)-1)*100, digits = 2),
           Term = gsub("analysis_covar", paste0(label, ": "), term)) %>% 
    select(Term, Estimate, 'Lower 95% CL', 'Upper 95% CL', 'P-value')
  view(tidy_results)

@@

d27 <- analysis_function("moisture_closest", "Wood moisture - closest to sampling")
d28 <- analysis_function("moisture_closest_2level", "Wood moisture - closest to sampling")
d29 <- analysis_function("mean_moisture_winter", "Wood moisture - Winter mean")
#d30 <- analysis_function("moisture_winter_2level", "Wood moisture - Winter mean")

### 2020-09-16 indoor_temp_rh_cleaning.Rmd
data cleaning and model updates

---
title: "KidsAIR indoor temp and humidity cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 23 June 2020"
output: pdf_document
---

@@

wmt_temp_rh <- temp_rh_initial_wmt %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         rh_indoor_current = as.numeric(RelHumCur),
         rh_indoor_max = as.numeric(RelHumMax),
         rh_indoor_min = as.numeric(RelHumMin),
         temp_indoor_current = as.numeric(TempCCur),
         temp_indoor_max = as.numeric(TempCMax),
         temp_indoor_min = as.numeric(TempCMin),
         area = "WMT") %>% 
  # replace -999 values with NA
  replace_with_na(replace = list(rh_indoor_current = -999, rh_indoor_max = -999,
                                 rh_indoor_min = -999, temp_indoor_current = -999,
                                 temp_indoor_max = -999, temp_indoor_min = -999)) %>% 
  replace_with_na(replace = list(rh_indoor_current = 0, rh_indoor_max = 0,
                                 rh_indoor_min = 0, temp_indoor_current = 0,
                                 temp_indoor_max = 0, temp_indoor_min = 0)) %>% 
  select(home_winter_id, area, rh_indoor_current, 
         rh_indoor_max, rh_indoor_min, temp_indoor_current, 
         temp_indoor_max, temp_indoor_min) %>% 
  arrange(home_winter_id)

@@

nn_temp_rh <- temp_rh_initial_nn %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         rh_indoor_current = as.numeric(RelHumCur),
         rh_indoor_max = as.numeric(RelHumMax),
         rh_indoor_min = as.numeric(RelHumMin),
         temp_indoor_current = as.numeric(TempCCur),
         temp_indoor_max = as.numeric(TempCMax),
         temp_indoor_min = as.numeric(TempCMin),
         area = "NN") %>% 
  # replace 0 and -999 values with NA
  replace_with_na(replace = list(rh_indoor_current = -999, rh_indoor_max = -999,
                                 rh_indoor_min = -999, temp_indoor_current = -999,
                                 temp_indoor_max = -999, temp_indoor_min = -999)) %>% 
  replace_with_na(replace = list(rh_indoor_current = 0, rh_indoor_max = 0,
                                 rh_indoor_min = 0, temp_indoor_current = 0,
                                 temp_indoor_max = 0, temp_indoor_min = 0)) %>% 
  select(home_winter_id, area, rh_indoor_current, 
         rh_indoor_max, rh_indoor_min, temp_indoor_current, 
         temp_indoor_max, temp_indoor_min) %>% 
  arrange(home_winter_id)

@@

ak_temp_rh <- temp_rh_initial_ak %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         rh_indoor_current = as.numeric(RelHumCur),
         rh_indoor_max = as.numeric(RelHumMax),
         rh_indoor_min = as.numeric(RelHumMin),
         temp_indoor_current = as.numeric(TempCCur),
         temp_indoor_max = as.numeric(TempCMax),
         temp_indoor_min = as.numeric(TempCMin),
         area = "AK") %>% 
  # replace -999 values with NA
  replace_with_na(replace = list(rh_indoor_current = -999, rh_indoor_max = -999,
                                 rh_indoor_min = -999, temp_indoor_current = -999,
                                 temp_indoor_max = -999, temp_indoor_min = -999)) %>% 
  replace_with_na(replace = list(rh_indoor_current = 0, rh_indoor_max = 0,
                                 rh_indoor_min = 0, temp_indoor_current = 0,
                                 temp_indoor_max = 0, temp_indoor_min = 0)) %>% 
  select(home_winter_id, area, rh_indoor_current, 
         rh_indoor_max, rh_indoor_min, temp_indoor_current, 
         temp_indoor_max, temp_indoor_min) %>% 
  arrange(home_winter_id)

@@

# Join temp/rh data from different areas
```{r}
wmt_temp_rh <- read_rds(paste0(file_path, "Output/wmt_temp_rh.rds"))
nn_temp_rh <- read_rds(paste0(file_path, "Output/nn_temp_rh.rds"))
ak_temp_rh <- read_rds(paste0(file_path, "Output/ak_temp_rh.rds"))

@@

indoor_temp_rh_clean <- kids_indoor_temp_rh %>% 
  mutate(area = as.factor(area)) %>% 
  right_join(kids_linked_ids, by = c("area", "home_winter_id"))

>>>>

---
title: "KidsAIR indoor temp and humidity cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 15 Sept 2020"
output: pdf_document
---

@@

wmt_temp_rh <- temp_rh_initial_wmt %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         rh_indoor_current = as.numeric(RelHumCur),
         rh_indoor_max = as.numeric(RelHumMax),
         rh_indoor_min = as.numeric(RelHumMin),
         temp_indoor_current = as.numeric(TempCCur),
         temp_indoor_max = as.numeric(TempCMax),
         temp_indoor_min = as.numeric(TempCMin),
         area = "WMT") %>% 
  # replace -999 values with NA
  replace_with_na(replace = list(rh_indoor_max = -999,
                                 rh_indoor_min = -999, 
                                 temp_indoor_max = -999, temp_indoor_min = -999)) %>% 
  replace_with_na(replace = list(rh_indoor_max = 0,
                                 rh_indoor_min = 0, 
                                 temp_indoor_max = 0, temp_indoor_min = 0)) %>% 
  select(home_winter_id, area, 
         rh_indoor_max, rh_indoor_min, 
         temp_indoor_max, temp_indoor_min) %>% 
  arrange(home_winter_id)

@@

nn_temp_rh <- temp_rh_initial_nn %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         rh_indoor_current = as.numeric(RelHumCur),
         rh_indoor_max = as.numeric(RelHumMax),
         rh_indoor_min = as.numeric(RelHumMin),
         temp_indoor_current = as.numeric(TempCCur),
         temp_indoor_max = as.numeric(TempCMax),
         temp_indoor_min = as.numeric(TempCMin),
         area = "NN") %>% 
  # replace 0 and -999 values with NA
  replace_with_na(replace = list(rh_indoor_max = -999,
                                 rh_indoor_min = -999, 
                                 temp_indoor_max = -999, temp_indoor_min = -999)) %>% 
  replace_with_na(replace = list(rh_indoor_max = 0,
                                 rh_indoor_min = 0, 
                                 temp_indoor_max = 0, temp_indoor_min = 0)) %>% 
  select(home_winter_id, area, 
         rh_indoor_max, rh_indoor_min, 
         temp_indoor_max, temp_indoor_min) %>% 
  arrange(home_winter_id)

@@

ak_temp_rh <- temp_rh_initial_ak %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         rh_indoor_current = as.numeric(RelHumCur),
         rh_indoor_max = as.numeric(RelHumMax),
         rh_indoor_min = as.numeric(RelHumMin),
         temp_indoor_current = as.numeric(TempCCur),
         temp_indoor_max = as.numeric(TempCMax),
         temp_indoor_min = as.numeric(TempCMin),
         area = "AK") %>% 
  # replace -999 values with NA
  replace_with_na(replace = list(rh_indoor_max = -999,
                                 rh_indoor_min = -999, 
                                 temp_indoor_max = -999, temp_indoor_min = -999)) %>% 
  replace_with_na(replace = list(rh_indoor_max = 0,
                                 rh_indoor_min = 0, 
                                 temp_indoor_max = 0, temp_indoor_min = 0)) %>% 
  select(home_winter_id, area, 
         rh_indoor_max, rh_indoor_min, 
         temp_indoor_max, temp_indoor_min) %>% 
  arrange(home_winter_id)

@@

# Join temp/rh data from different areas
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

wmt_temp_rh <- read_rds(paste0(file_path, "Output/wmt_temp_rh.rds"))
nn_temp_rh <- read_rds(paste0(file_path, "Output/nn_temp_rh.rds"))
ak_temp_rh <- read_rds(paste0(file_path, "Output/ak_temp_rh.rds"))

@@

indoor_temp_rh_clean <- kids_indoor_temp_rh %>% 
  mutate(area = as.factor(area)) %>% 
  right_join(kids_linked_ids, by = c("area", "home_winter_id")) %>% 
  mutate(rh_indoor_min2 = if_else(rh_indoor_min > rh_indoor_max, rh_indoor_max, rh_indoor_min),
         rh_indoor_max2 = if_else(rh_indoor_max < rh_indoor_min, rh_indoor_min, rh_indoor_max),
         temp_indoor_min2 = if_else(temp_indoor_min > temp_indoor_max, temp_indoor_max, temp_indoor_min),
         temp_indoor_max2 = if_else(temp_indoor_max < temp_indoor_min, temp_indoor_min, temp_indoor_max)) %>% 
  select(-rh_indoor_max, -rh_indoor_min, -temp_indoor_max, -temp_indoor_min) %>% 
  rename(rh_indoor_max = rh_indoor_max2,
         rh_indoor_min = rh_indoor_min2,
         temp_indoor_max = temp_indoor_max2,
         temp_indoor_min = temp_indoor_min2)

### 2020-09-16 indoor_temp_rh_summary.Rmd
data cleaning and model updates

```{r}
# Load data
indoor_temp_rh_clean <- read_rds("Output/indoor_temp_rh_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

```{r, include=FALSE}
temp_rh_summary <- indoor_temp_rh_clean %>%
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize_if(is.numeric, list(mean = mean, sd = sd, min = min, 
                                med = median, max = max), na.rm = TRUE) %>% 
  select(-area) %>% 
  t() 
kable(temp_rh_summary, col.names = c("Alaska", "Navajo", "Montana"), 
      digits = 1, align = "c")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds"))
```

```{r, include=FALSE}
temp_rh_summary <- health_exposure_data_sampling_day %>%
  select(area, home, home_winter_id, winter_id, 
         temp_indoor_max, temp_indoor_min, rh_indoor_max, rh_indoor_min) %>% 
  mutate(temp_diff = if_else(temp_indoor_min > temp_indoor_max, 1, 0),
         rh_diff = if_else(rh_indoor_min > rh_indoor_max, 1, 0)) %>% 
  filter(!is.na(temp_diff)) %>% 
  distinct(area, home_winter_id, .keep_all = TRUE)
```

### 2020-09-16 manuscript_tables_figures.Rmd
data cleaning and model updates

>>>>

```{r}
# Summary data for results letters to send to participants

home_summary <- health_exposure_data_sampling_day %>% 
  group_by(home) %>% 
  arrange(home, sampling_day) %>% 
  select(area, home, winter_id, pm_mean_sampling_period, pm_mean_sampling_day, 
         rh_indoor_min, rh_indoor_max) %>% 
  mutate(daily_min = min(pm_mean_sampling_day, na.rm = TRUE),
         daily_max= max(pm_mean_sampling_day, na.rm = TRUE)) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  replace_with_na_all(condition = ~.x %in% c("Inf", "-Inf")) %>% 
  mutate("Min RH (%)" = if_else(rh_indoor_min > rh_indoor_max, rh_indoor_max, rh_indoor_min),
         "Max RH (%)" = if_else(rh_indoor_max < rh_indoor_min, rh_indoor_min, rh_indoor_max)) %>% 
  arrange(area, home) %>% 
  mutate("Mean PM2.5 (ug/m3)" = round(pm_mean_sampling_period, digits = 1),
         "Min PM2.5 (ug/m3)" = round(daily_min, digits = 1),
         "Max PM2.5 (ug/m3)" = round(daily_max, digits = 1),
         check = if_else(`Min RH (%)` > `Max RH (%)`, 1, 0)) %>% 
  select(-rh_indoor_min, -rh_indoor_max, -pm_mean_sampling_period, -check,
         -daily_min, -daily_max) %>% 
  rename(Area = area,
         Home = home,
         Winter = winter_id)

write_csv(home_summary, paste0(file_path, "Output/kids_letter_data.csv"), na = "")
```

### 2020-09-16 merge_datasets.Rmd
data cleaning and model updates

---
title: "KidsAIR: merge exposure datasets"
author: "Ethan Walker"
date: "Started 24 March 2020, Updated 26 June 2020"
output: pdf_document
---

@@

@@

analysis_data4 <- indoor_temp_rh_clean %>% 
  filter(winter_id == 1) %>% 
  mutate(winter_id = as.character(winter_id)) %>%
  select(area, home, home_winter_id, winter_id, treatment_assigned, treatment_actual, 
         rh_indoor_current:temp_indoor_min) %>% 
  ungroup() %>% 
  right_join(analysis_data3, by = c("area", "home", "home_winter_id", "winter_id", 
                                    "treatment_assigned", "treatment_actual")) %>% 
  mutate(temp_max_5 = temp_indoor_max/5,
         temp_min_5 = temp_indoor_min/5,
         rh_max_5 = rh_indoor_max/5,
         rh_min_5 = rh_indoor_min/5) %>% 
  ungroup() %>% 
  arrange(area, home, home_winter_id, sample_date)

>>>>

---
title: "KidsAIR: merge exposure datasets"
author: "Ethan Walker"
date: "Started 24 March 2020, Updated 15 Sept 2020"
output: pdf_document
---

@@

#write_rds(pm_sums_joined3, paste0(file_path, "Output/pm_sums_joined3.rds"))
pm_sums_joined3 <- read_rds(paste0(file_path, "Output/pm_sums_joined3.rds"))

@@

analysis_data4 <- indoor_temp_rh_clean %>% 
  filter(winter_id == 1) %>% 
  mutate(winter_id = as.character(winter_id)) %>%
  select(area, home, home_winter_id, winter_id, treatment_assigned, treatment_actual, 
         rh_indoor_min:temp_indoor_max) %>% 
  ungroup() %>% 
  right_join(analysis_data3, by = c("area", "home", "home_winter_id", "winter_id", 
                                    "treatment_assigned", "treatment_actual")) %>% 
  mutate(temp_max_5 = temp_indoor_max/5,
         temp_min_5 = temp_indoor_min/5,
         rh_max_5 = rh_indoor_max/5,
         rh_min_5 = rh_indoor_min/5) %>% 
  ungroup() %>% 
  arrange(area, home, home_winter_id, sample_date)

### 2020-09-16 stove_grade_usage_cleaning.Rmd
data cleaning and model updates

##### WMT #####
# Load data
stove_grades_initial_wmt <- read_csv(paste0(file_path, "Input/WMT/stove.csv"), 
                                  na = c("NULL", ""))

wmt_stove_grades <- stove_grades_initial_wmt %>% 
  # rename variables
  mutate(home_id = as.factor(HomeID),
         home_winter_id = as.factor(HomeWinterID),
         stove_grade = as.factor(Score1),
         area = "WMT") %>% 
  select(home_id, home_winter_id, area, stove_grade) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

@@

##### NN #####
# Load data
stove_grades_initial_nn <- read_csv(paste0(file_path, "Input/NN/stove.csv"), 
                                  na = c("NULL", ""))

nn_stove_grades <- stove_grades_initial_nn %>% 
  # rename variables
  mutate(home_id = as.factor(HomeID),
         home_winter_id = as.factor(HomeWinterID),
         stove_grade = as.factor(Score1),
         area = "NN") %>% 
  select(home_id, home_winter_id, area, stove_grade) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

@@

##### AK #####
# Load data
stove_grades_initial_ak <- read_csv(paste0(file_path, "Input/AK/stove.csv"), 
                                  na = c("NULL", ""))

ak_stove_grades <- stove_grades_initial_ak %>% 
  # rename variables
  mutate(home_id = as.factor(HomeID),
         home_winter_id = as.factor(HomeWinterID),
         stove_grade = as.factor(Score1),
         area = "AK") %>% 
  select(home_id, home_winter_id, area, stove_grade) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

@@

# Join stove grade data from different areas
```{r}
wmt_stove_grades <- read_rds(paste0(file_path, "Output/wmt_stove_grades.rds"))
nn_stove_grades <- read_rds(paste0(file_path, "Output/nn_stove_grades.rds"))
ak_stove_grades <- read_rds(paste0(file_path, "Output/ak_stove_grades.rds"))

@@

stove_grades_clean <- kids_stove_grades %>% 
  mutate(area = as.factor(area)) %>% 
  filter(home_id != 0) %>% 
  # Mark gave a couple of "D" grades when there was not enough info to score the stove
  # removing those "D" grades from final dataset
  filter(stove_grade != "D") %>% 
  select(-home_id) %>% 
  right_join(kids_linked_ids, by = c("area", "home_winter_id")) %>% 
  arrange(area, home, winter_id)

>>>>

##### WMT #####
# Load data
stove_grades_initial_wmt <- read_xlsx(paste0(file_path, "Input/WMT/stove.xlsx"), 
                                  na = c("NULL", ""))

wmt_stove_grades <- stove_grades_initial_wmt %>% 
  # rename variables
  mutate(home_id = as.factor(HomeID),
         home_winter_id = as.factor(HomeWinterID),
         stove_grade = as.factor(Score1),
         area = "WMT") %>% 
  select(home_id, home_winter_id, area, stove_grade) %>% 
  ungroup() %>% 
  arrange(home_winter_id) %>% 
  filter(!is.na(stove_grade)) %>% 
  filter(home_id != 0 & home_id != 999)

@@

##### NN #####
# Load data
stove_grades_initial_nn <- read_xlsx(paste0(file_path, "Input/NN/stove.xlsx"), 
                                  na = c("NULL", ""))

nn_stove_grades <- stove_grades_initial_nn %>% 
  # rename variables
  mutate(home_id = as.factor(HomeID),
         home_winter_id = as.factor(HomeWinterID),
         stove_grade = as.factor(Score1),
         area = "NN") %>% 
  select(home_id, home_winter_id, area, stove_grade) %>% 
  ungroup() %>% 
  arrange(home_winter_id) %>% 
  filter(!is.na(stove_grade)) %>% 
  filter(home_id != 0 & home_id != 999)

@@

##### AK #####
# Load data
stove_grades_initial_ak <- read_xlsx(paste0(file_path, "Input/AK/stove.xlsx"), 
                                  na = c("NULL", ""))

ak_stove_grades <- stove_grades_initial_ak %>% 
  # rename variables
  mutate(home_id = as.factor(HomeID),
         home_winter_id = as.factor(HomeWinterID),
         stove_grade = as.factor(Score1),
         area = "AK") %>% 
  select(home_id, home_winter_id, area, stove_grade) %>% 
  ungroup() %>% 
  arrange(home_winter_id) %>% 
  filter(!is.na(stove_grade)) %>% 
  filter(home_id != 0 & home_id != 999)

@@

# Join stove grade data from different areas
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

wmt_stove_grades <- read_rds(paste0(file_path, "Output/wmt_stove_grades.rds"))
nn_stove_grades <- read_rds(paste0(file_path, "Output/nn_stove_grades.rds"))
ak_stove_grades <- read_rds(paste0(file_path, "Output/ak_stove_grades.rds"))

@@

stove_grades_clean <- kids_stove_grades %>% 
  mutate(area = as.factor(area)) %>% 
  # Mark gave a couple of "D" grades when there was not enough info to score the stove
  # removing those "D" grades from final dataset
  filter(stove_grade != "D") %>% 
  select(-home_id) %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>% 
  arrange(area, home, winter_id)
